### 2020-01-23 experiments.tex
py
python

@@

\subsubsection{Original Program Selection}

@@

@@

\begin{enumerate}
\item {\bf Boolean constant misuse:}  This detector flags code like {\tt if (true)} or {\tt g(b || true)} (where {\tt g} is a function that takes a Boolean input).  Constant-valued conditionals tend to indicate debugging efforts that have persisted into production code, or other faults; there are almost no circumstances where a conditional should not vary with state or input.  This detector is actually split into two detectors, one for this serious issue, and an informational/stylistic detector that notes that code such as {\tt if (x == true)}, while semantically harmless, is difficult to read.  This problem was easily identified from cases such as this mutant, killed by SmartCheck but not Slither:

\begin{code}
0x598ab825d607ace3b00d8714c0a141c7ae2e6822\_Vault.mutant.275.sol: 424contracts//0x598ab825d607ace3b00d8714c0a141c7ae2e6822\_Vault.sol:249
        if (!p.recipient.send(p.amount)) \{  // Make the payment
 ==>          if (true) \{  // Make the payment
        if (true) \{  // Make the payment
\end{code}

\item {\bf Type-based tautologies:}  A type-based tautology is again a case where a Boolean expression has a constant value, but this is not due to misuse of a Boolean constant, but is instead due to the \emph{types} in a comparison.  For example, if {\tt x} is an unsigned integer type, the comparison {\tt x >= 0} is always true and {\tt x < 0} is always false.  This detector is a generalization of the SmartCheck detector \url{https://github.com/smartdec/smartcheck/blob/master/rule_descriptions/SOLIDITY_UINT_CANT_BE_NEGATIVE/description_en.html}, modified to actually compute the ranges of types and identify more general instances of tautological comparisons, e.g. {\tt y < 512} where {\tt y}'s type is {\tt int8}.  Again, the problem was easily identified by a mutants killed by SmartCheck but not Slither such as:

\begin{code}
0x968815CD73647C3af02a740a2438D6f8219e7534\_TTPresale.mutant.311.sol: 424contracts//0x968815CD73647C3af02a740a2438D6f8219e7534\_TTPresale.sol:175
        require(nextDiscountTTMTokenId6 >= 361 \&\& nextDiscountTTMTokenId6 <= 391);
 ==>  ...361...==>...0...
        require(nextDiscountTTMTokenId6 >= 0 \&\& nextDiscountTTMTokenId6 <= 391);
\end{code}

\item {\bf Loss of precision due to divide before multiply:}  Solidity only supports integer types.  This means that performing division before multiplication can introduce rounding that is not present when the multiplication is performed first.  This is a fairly important problem, given the frequency with which Solidity code performs financial calculations where maximum precision is desired.  SmartCheck provides a detector for such precision losses \url{https://github.com/smartdec/smartcheck/blob/master/rule_descriptions/SOLIDITY_DIV_MUL/description_en.html}, which enabled it to detect mutants such as:

\begin{code}
0x534ccee849a688581d1b0c65e7ff317ed10c5ed3\_NametagToken.mutant.480.sol: 424contracts//0x534ccee849a688581d1b0c65e7ff317ed10c5ed3\_NametagToken.sol:650
        byte char = byte(bytes32(uint(x) * 2 ** (8 * j)));
 ==>  ...*...==>.../...
        byte char = byte(bytes32(uint(x) * 2 ** (8 / j)));
\end{code}

\end{enumerate}

@@

\subsubsection{Original Program Selection}

@@

>>>>

\subsubsection{Static Analysis Tools Compared}

@@

\subsubsection{Smart Contract Selection}

@@

\begin{figure}
  {\scriptsize
\begin{code}
  0x598ab825d607ace3b00d8714c0a141c7ae2e6822\_Vault.mutant.275.sol:
  424contracts/0x598ab825d607ace3b00d8714c0a141c7ae2e6822\_Vault.sol:249
        if (!p.recipient.send(p.amount)) \{  // Make the payment
 ==>          if (true) \{  // Make the payment
        if (true) \{  // Make the payment
      \end{code}
      }
      \caption{Mutant showing {\bf Boolean constant misuse}.}
      \label{fig:boolean}
    \end{figure}

    \begin{figure}
      {\scriptsize
\begin{code}
  0x968815CD73647C3af02a740a2438D6f8219e7534\_TTPresale.mutant.311.sol:
  424contracts/0x968815CD73647C3af02a740a2438D6f8219e7534\_TTPresale.sol:175
        require(nextDiscountTTMTokenId6 >= 361 \&\& nextDiscountTTMTokenId6 <= 391);
 ==>  ...361...==>...0...
        require(nextDiscountTTMTokenId6 >= 0 \&\& nextDiscountTTMTokenId6 <= 391);
      \end{code}
      }
      \caption{Mutant showing {\bf Type-based tautologies}.}
      \label{fig:tautology}      
\end{figure}

\begin{figure}
  {\scriptsize
\begin{code}
  0x534ccee849a688581d1b0c65e7ff317ed10c5ed3\_NametagToken.mutant.480.sol:
  424contracts/0x534ccee849a688581d1b0c65e7ff317ed10c5ed3\_NametagToken.sol:650
        byte char = byte(bytes32(uint(x) * 2 ** (8 * j)));
 ==>  ...*...==>.../...
        byte char = byte(bytes32(uint(x) * 2 ** (8 / j)));
      \end{code}
      }
      \caption{Mutant showing {\bf Loss of precision}.}
      \label{fig:divmul}            
      \end{figure}

@@

\begin{enumerate}
\item {\bf Boolean constant misuse:}  This detector flags code like {\tt if (true)} or {\tt g(b || true)} (where {\tt g} is a function that takes a Boolean input).  Constant-valued conditionals tend to indicate debugging efforts that have persisted into production code, or other faults; there are almost no circumstances where a conditional should not vary with state or input.  This detector is actually split into two detectors, one for this serious issue, and an informational/stylistic detector that notes that code such as {\tt if (x == true)}, while semantically harmless, is difficult to read.  This problem was easily identified from cases such as the mutant in Figure \ref{fig:boolean}, killed by SmartCheck but not Slither:

\item {\bf Type-based tautologies:}  A type-based tautology is again a case where a Boolean expression has a constant value, but this is not due to misuse of a Boolean constant, but is instead due to the \emph{types} in a comparison.  For example, if {\tt x} is an unsigned integer type, the comparison {\tt x >= 0} is always true and {\tt x < 0} is always false.  This detector is a generalization of the SmartCheck detector \url{https://github.com/smartdec/smartcheck/blob/master/rule\_descriptions/SOLIDITY\_UINT\_CANT\_BE\_NEGATIVE/description\_en.html}, modified to actually compute the ranges of types and identify more general instances of tautological comparisons, e.g. {\tt y < 512} where {\tt y}'s type is {\tt int8}.  Again, the problem was easily identified by mutants killed by SmartCheck but not Slither such as the one in Figure \ref{fig:tautology}.

\item {\bf Loss of precision:}  Solidity only supports integer types.  This means that performing division before multiplication can introduce rounding that is not present when the multiplication is performed first.  This is a fairly important problem, given the frequency with which Solidity code performs financial calculations where maximum precision is desired.  SmartCheck provides a detector for such precision losses \url{https://github.com/smartdec/smartcheck/blob/master/rule\_descriptions/SOLIDITY\_DIV\_MUL/description\_en.html}, which enabled it to detect mutants such as the one shown in Figure\ref{fig:divmul}.
\end{enumerate}

@@

\subsubsection{Static Analysis Tools Compared}

\subsubsection{Project Selection}

@@

\subsubsection{Static Analysis Tools Compared}

\subsubsection{Project Selection}

\begin{figure}
  \includegraphics[width=\columnwidth]{python.png}
  \caption{Mutants killed by Python static analysis tools.}
  \label{fig:pythonvenn}
\end{figure}

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & \multicolumn{2}{|c|}{Findings} & \multicolumn{2}{|c|}{Mutation Score}  & Mutant \\
    Tool & Mean & Median & Mean & Median & Ratio\\
    \hline
    \hline
    Pylint & 2.24 & 1.00 & 0.22 & 0.20 & 0.097 \\
    \hline
    pyflakes & 2.4 & 1.00 & 0.03 & 0.00 & 0.012 \\
    \hline
    PyChecker & 0.56& 0.00 & 0.10 & 0.00 &  0.183 \\
    \hline
  \end{tabular}
  \caption{Python tools: number of findings and mutation scores over all projects.}
  \label{tab:scorepython}
\end{table}

\begin{table}
  \begin{tabular}{l|r|r|r}
    & & \multicolumn{2}{|c|}{} \\
    & \# Clean & \multicolumn{2}{|c|}{Mutation Score} \\
    Tool & Projects & Mean & Median \\
    \hline
    \hline
    Pylint & 0 & N/A & N/A \\
    \hline
    pyflakes & 12 & 0.02 & 0.00 \\
    \hline
    PyChecker & 21& 0.01 & 0.00 \\
    \hline
  \end{tabular}
  \caption{Python tools: clean project counts and mutation scores.}
  \label{tab:cleanpython}
\end{table}
